Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-27 docs/paper.tex
Broke up problem definition into three parts, condensed formal MAPF statement

	In CBM, the Meta-Agent variant of CBS \cite{sharon2015} is used as a high-level search framework; in the low-level search, single teams are planned in polynomial time as constrained anonymous MAPF instances using a max-flow approach \cite{yu2013}. The experimental results reported in \cite{ma2016} indicate that CBM scales well as the number of agents and the sizes of teams increase; although in addition to grid instances with 10\% of tiles being blocked, Kiva \cite{wurman2007} instances are also solved, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios, such as those included in the Moving AI benchmarks \cite{sturtevant2012} for MAPF.

@@

	Multi-agent pathfinding with matching is a generalization of multi-agent pathfinding, the problem of finding paths for multiple agents without any conflicts. 
	\subsection{Multi-agent pathfinding}

	Formally, a MAPF instance can be described as follows. Let $G = (V,E)$ be an undirected graph, with each $v\in V$ representing an obstacle-free tile on a 4-connected grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles. Let there be $k$ agents $a_1,\ldots,a_k$ with starting locations $s_1,\ldots,s_k$ and goals $g_1,\ldots,g_k$. For each agent $a_i$, a path $\pi_i$ from $s_i$ to $g_i$ is to be found such that all agents' paths $\pi_i$ taken together are non-conflicting and therefore are a solution. In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts and no edge conflicts, as shown in Figure \ref{fig:conflicts}. Letting $\pi_i^t$ denote the $t$'th node of path $\pi_i$, this means that for $i\neq j$, for all $t$, $\pi_i^t\neq \pi_j^t$ and $(\pi_i^t \neq \pi_j^{t + 1})\lor(\pi_i^{t+1} \neq \pi_j^t)$. Given a solution $(\pi_1,\ldots,\pi_k)$, a vector of per-agent costs $(c_1,\ldots,c_k)$ can be found. For $\pi_i$, $c_i$ is defined as the time at which $a_i$ reaches $g_i$ for the last time and remains there, meaning that for $t \geq c_i$, $\pi_i^{t} = g_i$. One property of $c_i$ is that $c_i \geq c^*_i$ where $c^*_i$ is defined as the cost of $\pi^*_i$, the shortest path from $s_i$ to $g_i$ that can be computed using any optimal pathfinding algorithm. Using this terminology, the two common objectives for MAPF can be restated as follows:
	\begin{itemize}
		\item Makespan: $\max_{i} c_i$
		\item Sum of individual costs (SIC): $\sum_i c_i$
	\end{itemize}
	In this work, an optimal solution is defined as having minimal SIC.

	\begin{wrapfigure}[10]{R}{.35\textwidth}
		\vspace{-10pt}
		\centering
		\includegraphics[width=\linewidth]{img/symmetries}
		\caption{Symmetric paths on a 4-connected grid \cite{harabor2010}.}
		\label{fig:symmetries}
	\end{wrapfigure}

	The mapping from $(\pi_1,\ldots,\pi_k)$ to a SIC is surjective: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$. On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths \cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods such as Jump Point Search \cite{harabor2011} are used to speed up the search. In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.

>>>>

	In CBM, the Meta-Agent variant of CBS \cite{sharon2015} is used as a high-level search framework; in the low-level search, single teams are planned in polynomial time as constrained anonymous MAPF instances using a max-flow approach \cite{yu2013}. The experimental results reported in \cite{ma2016} indicate that CBM scales well as the number of agents and the sizes of teams increase; although in addition to grid instances with 10\% of tiles being blocked, Kiva \cite{wurman2007} instances are also solved, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios such as the Moving AI maps \cite{sturtevant2012}.

@@

	A MAPF instance can be defined as follows. Let $G = (V,E)$ be an undirected graph, with each $v\in V$ representing an obstacle-free tile on a 4-connected grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles. Let there be $k$ agents $a_1,\ldots,a_k$ with starting locations $s_1,\ldots,s_k$ and goals $g_1,\ldots,g_k$. For each agent $a_i$, a path $\pi_i$ from $s_i$ to $g_i$ is to be found such that all agents' paths $\pi_i$ taken together are non-conflicting and therefore are a solution. In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts and no edge conflicts, as shown in Figure \ref{fig:conflicts}. Letting $\pi_i^t$ denote the $t$'th node of path $\pi_i$, this means that for $i\neq j$, for all $t$, $\pi_i^t\neq \pi_j^t$ and $(\pi_i^t \neq \pi_j^{t + 1})\lor(\pi_i^{t+1} \neq \pi_j^t)$. To achieve this, agent $a_i$ may also wait ($\pi_i^t = \pi_i^{t+1}$) instead of moving to a grid neighbor. Given a solution $(\pi_1,\ldots,\pi_k)$, a vector of per-agent costs $(c_1,\ldots,c_k)$ can be found. For $\pi_i$, $c_i$ is defined as the time at which $a_i$ reaches $g_i$ for the last time, meaning that for $t \geq c_i$, $\pi_i^{t} = g_i$. 
	For each $c_i$, $c_i \geq c^*_i$ where $c^*_i$ is defined as the cost of a shortest path from $s_i$ to $g_i$. 
	\subsection{Objectives for MAPF}

	Using the established terminology, the two common objectives for MAPF can be restated as follows:
	\begin{itemize}
		\item Makespan: $\max_{i} c_i$
		\item Sum of individual costs (SIC): $\sum_i c_i$
	\end{itemize}
	In this work, an optimal solution is defined as having minimal SIC.

	\begin{wrapfigure}[10]{R}{.35\textwidth}
		\vspace{-10pt}
		\centering
		\includegraphics[width=\linewidth]{img/symmetries}
		\caption{Symmetric paths on a 4-connected grid \cite{harabor2010}.}
		\label{fig:symmetries}
	\end{wrapfigure}
	The mapping from $(\pi_1,\ldots,\pi_k)$ to a SIC is surjective: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$. On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths \cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods such as Jump Point Search \cite{harabor2011} are used to speed up the search. In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.
